\makeatletter
\def\input@path{{../}}
\makeatother
\documentclass[../main.tex]{subfiles}
\begin{document}
\renewcommand{\path}{3_chapter_1/}
\chapter[Toy Modelling for teaching and developing Methodology]{Using simple Models to understand and develop Methodology - Ensembler
    \footnote{\label{footnoteChapter1CopyRight} 
    Reprinted (adapted) with permission from Benjamin Ries, Stephanie M. Linker, David F. Hahn, Gerhard König and Sereina Riniker ,
    J. Chem. Inf. Model., \textbf{61}, 560-564 (2021). Copyright 2021 American Chemical Society.}
}
\chaptermark{Free Energy Calculation}
\label{ch:feens}

\aquote{
"It all works because Avogadro's number is closer to infinity than to 10."
}{R. Baierlein; Gromacs quote collection \cite{Abraham2015}}




\begin{abstract}
Ensembler is a python package that allows for fast and easy access to the simulation of one and two-dimensional model systems.
It enables method development using small test systems and to deepen the understanding of a broad spectrum of molecular dynamics (MD) methods, starting from basic techniques to enhanced sampling and free-energy calculations.
The ease of installing and using the package increases shareability, comparability, and reproducibility of scientific code developments.
Here, we provide a description of the implementation and usage of the package as well as an application example for free-energy calculation.
The code of Ensembler is freely available on GitHub \textit{https://github.com/rinikerlab/Ensembler}.
%

\end{abstract}

\clearpage
\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%================================================================================
\section{Introduction}
%================================================================================

\input{3_chapter_1/inc/intro.tex}

%================================================================================
\section{Theory}
%================================================================================

\input{3_chapter_1/inc/theory.tex}

%================================================================================
\section{Results and Discussion}
%================================================================================

\input{3_chapter_1/inc/results.tex}

\clearpage
\newpage

%================================================================================
\section{Conclusion}
%================================================================================

\input{3_chapter_1/inc/conclusion.tex}

\clearpage
\pagebreak


\bibliography{MendeleyMerge.bib}

\end{document}
