\chapter{Acknowledgements}
This thesis would not have been possible without many people who have
supported me over the last few years. I will try to list many of them here.

%supervisor
I deeply want to thank my supervisor Prof. Sereina Riniker. Thank you for giving me the opportunity to work on fascinating projects and develop my ideas. I admire your disciplined and efficient project management. Your patience and straightforward approach to science taught me a lot. I also want to thank you for listening when times were rough, and matters were not science-related.
I would like to express my gratitude to Prof. Philippe H{\ "u}nenberger: Thank you for inspiring me with your endless creativity and authentic way of handling science.
I would also like to thank my co-examiner, Prof. Niels Hansen, for the great lecture about free energy calculations and that he accepted to examine this thesis.


%Group
I want to thank the combined groups of computational chemistry (CCG) and Computer Simulation of Molecular Systems (CSMS) for the great atmosphere and the activities we could do together. It is a shame that the Covid pandemic pushed us to the home office and forced us to reduce the activities.
Specifically, I would like to thank the following people (lexicographically sorted):
Alzbeta Kubincova, for the great ice-skating events and the fantastic hackathon project we did together.
Anick Rennevey, for the introduction into the computer system of IGC and for sharing the incredible Asian food.
Anna Albertini, for the cool shared teaching experience and for being the new organizer of the CCCCP.
Candide Champion,  for the discussions and the great hike to the grosser Mythen.
Carmen Esposito, for the coffee, with discussions about PCAs and the great group opera visits.
David Hahn, for the great discussions about free energy calculations and initial spark and work towards the Ensembler package.
Dominik Sidler, for the fabulous group weekend at the Bettmeralp and teaching me the value of constructing theory.
Emilia P. Barros, for the great discussions about EoffRebalancing and beautiful fairytale-like places in Switzerland.
Felix Pultar for the discussions about PyGromosTools, and I hope you find it a convenient tool.
Greg Landrum, for sharing his knowledge and experience in cheminformatics.
M. M. Gregor Weiss, for sharing the office with me, his passion for coding, exploring the clustering space together, and our mountain bike tours.
Gerhard K{\"o}nig we had an exciting start that resulted in great collaboration, many beautiful coffee sessions, and discussions about high german.
Jagna Witek, for giving me an excellent start to Zurich and introducing me to the theory of the Markov state modeling for macrocycles.
Jessica Braun it was a pleasure meeting you, and I'm greatly cheered up to share the same liberal definition for APIs with you.
Lennard B{\"o}selt, I enjoyed having discussions about a possible transition EDS with you, finding similarities in our families, and I am happy having convinced you of IDEs.
Marc Lehner, for the introduction to the alpine world, seeing potential in the convenient PyGromosTools and sharing the swiss culture with me.
Moritz Th{\"u}rliman, for the great discussions about neuronal networks, politics, and reviving my passion for literature.
Paul Katzberger, for the political status report of Austria and his fascination for Numba (which, of course, will lead to me learning more about it).
Patrick Bleiziffer, for the help with the partial charge calculations for the 3D-PSAs.
Sadra Kashef ol Gheta, for the great philosophical conversations.
Marina Pereira Oliviera, for excellent soccer games and introducing her beautiful dog Lua to us.
Salom{\'e} Rieder, thanks for the productive discussions, and I enjoyed the collaborative work together with you.
Shuzhe Wang, for the good questions and discussions.
Stephanie Linker, for the mood uplifting and motivating discussions, that were a great asset and always cleared up grey days.
Thomas Stadelmann, for a great time with semi-peptidic macrocycles and the excellent sarcastic humor.



%%% Students
I want to thank Kay Shaller, Clemens Rhiner, Karl Normak, and Theo Smertnig, the students I supervised, for your work. You did contribute fundamentally to our research, and I'm proud to have been a part of your studies.

I want to especially thank our collaborators at the University de Sherbrooke Christian Comeau and {\' E}ric Marsault, who sadly passed away during the collaboration.

I also want to thank Prof. Chris Oostenbrink for the support with the Gromos Gitlab, and I hope that the GROMOS family will make it open source soon for the future of GROMOS.


%% Secretay
Dear Claudia Hilty, thanks for your fast and always competent support. And the members of the group of Prof. Reiher for beautiful after-work activities.

%% Previous
I want to acknowledge Prof. van der Spoel, Nina Fischer, Philip Thiel, and Prof. Kohlbacher, who opened the door to Molecular dynamics simulations for me. I'm very thankful for their support and advice.  
Mohammad Mehdi Ghahremanpour, I want to thank you for your advice and support that encouraged me on my path.

%% Societies
I don't want to forget the societies where I could interact with many different people.
Dear VAC, being your dragon counting the coin or organizing hikes with you was a pleasure. I want to mention Danylo Matselyukh and Agathe Vanas especially. 
Dear YoungSCS and especially the Board of 2020, it was a wonderful experience to meet all of you and reboot YoungSCS together with you as president. In my first year with youngSCS, we started with five people at the general assembly. After two years, we achieved 20 active people with a general assembly of 80 people and many events organized by youngSCS, which I consider a great success of the Board. I especially want to mention Eva Vandale, Melanie Gut, Ahmed Elabd, Stephanie Linker, Patrick Fritz, Marie D{\`e}sir{\`e}e Scheidt, Marie Perrin, and Lluc Farrera-Soler

%% Freunde / Family
Last but not least, I want to thank Dennis, Unn Beate \& Edwin, Barbara, Enes, Viktoria, Andr{\'e} and Alexander for their friendship, which I deeply value.
I'm sincerely grateful for the support of my family and my wife.

\begin{center}
    \begin{minipage}[t]{.5\linewidth}
        \aquote{
            "I wett das du nach de stärne griffsch\\
            Gliich wie wiit entfärnt si si\\
            Das du dänksch lachsch läbsch,\\
            Wiu die zit goht schnäu verbi\\
            Lueg das du nach de stärne griffsch\\
            Gliich wie wiit entfärnt si si \\
            ..."
            }{Manillio, Stärne, Jede Tag Superstar}
    \end{minipage}
\end{center}
