\chapter{Publications}
\noindent \textbf{Articles in peer-reviewed journals:}
\begin{enumerate}
\item B.\ Ries, S.\ M.\ Linker, D.\ F.\ Hahn, G.\ K\"onig, S.\ Riniker, Ensembler: A Simple Package for Fast Prototyping and Teaching Molecular Simulations, {\em J. Chem. Inf. Model.}, \textbf{61}, 560--564 (2021).

\item B.\ Ries$^\dag$, S.\ Rieder$^\dag$, C.\ Rhiner, Philippe H. H\"unenberger, S.\ Riniker, A Graph-Based Approach to the Restraint Problem in Dual Topology Approaches with RestraintMaker, {\em  J. Comput.-Aided Mol. Des.}, submitted (2021).

\item B.\ Ries, K.\ Normak, R. G.\ Wei\ss, S.\ Rieder, C.\ Candide, G. K\"onig, S.\ Riniker, Relative Free-Energy Calculations for Scaffold Hopping-Type Transformations with an Automated RE-EDS Sampling Procedure, {\em J. Comput.-Aided Mol. Des.}, in press (2021).

\item C.\ Comeau$^\dag$, B.\ Ries$^\dag$, T.\ Stadelmann, J.\ Tremblay, S.\ Poulet, U.\ Fröhlich, J.\ Côté, P.\ Boudreault, R.\ M.\ Derbali, P.\ Sarret, M.\ Grandbois, G.\ Leclair, S.\ Riniker, \'E.\ Marsault, Modulation of the Passive Permeability of Semipeptidic Macrocycles: N- and C-Methylations Fine-Tune Conformation and Properties, {\em J. Med. Chem.}, \textbf{64}, 5365--5383 (2021).
\end{enumerate}
\noindent $^\dag$ These authors contributed equallly. \\

\newpage
\noindent \textbf{Related publications:}
\begin{enumerate}
    \item J.\ Witek, S.\ Wang, B.\ Schroeder, R.\ Lingwood, A.\ Dounas, H.\ Roth, M.\ Fouché, M.\ Blatter, O.\ Lemke, B.\ Keller, and S.\ Riniker, Rationalization of the Membrane Permeability Differences in a Series of Analogue Cyclic Decapeptides, {\em J. Chem. Inf. Model.}, \textbf{59}, 294--308 (2019).
    \item  G.\ K\"onig, N.\ Glaser, B.\ Schroeder, A.\ Kubincová, P.\ H.\ H\"unenberger, S.\ Riniker, An Alternative to Conventional $\lambda$-Intermediate States in Alchemical Free Energy Calculations: $\lambda$-Enveloping Distribution Sampling, {\em J. Chem. Inf. Model.}, \textbf{60}, 5407--5423 (2020).
    \item R.\ G.\ Wei\ss, B.\ Ries, S.\ Wang, S.\ Riniker, Volume-Scaled Common Nearest Neighbor Clustering Algorithm with Free-Energy Hierarchy , {\em J. Chem. Phys.}, \textbf{154}, 084106 (2021).
    \item S.\ M.\ Linker, S.\ Wang, B.\ Ries, T.\ Stadelmann, S.\ Riniker, Passing the Barrier – How Computer Simulations Can Help to Understand and Improve the Passive Membrane Permeability of Cyclic Peptides, {\em CHIMIA}, \textbf{75}, 518--521 (2021).
    \item G.\ K\"onig, B.\ Ries, P.\ H.\ H\"unenberger, S.\ Riniker, Efficient Alchemical Intermediate States in Free Energy Calculations Using  $\lambda$-EDS, {\em J. Chem. Inf. Model.}, \textbf{17}, 5805--5815 (2021).
    \item S.\ M.\ Linker, C.\ Schellhaas, B.\ Ries, and S.\ Riniker, Membrane-Like Interfaces Facilitate Conformational Closure for Passive Permeability of Cyclic Peptides, {\em RSC Adv.}, submitted (2021).
    \item E.\ P.\ Barros, B.\ Ries, L.\ B\"oselt, C.\ Champion, P.\ H.\ H\"unenberger, S.\ Riniker, Recent Developments in Multiscale Free Energy Simulations, {\em Curr. Opin. Struct. Biol.}, \textbf{72}, 55--62 (2022).
    %\item S. Rieder, B.\ Ries, K.\ Schaller, C.\ Champion,  E.\ P.\ Barros,  S.\ Riniker {\em xxxxxx} ({\bf submitted}): Relative Hydration Free Energy Calculations Using GAFF Topologies for Large Sets of Molecules with RE-EDS
    %\item B.\ Ries, L.\ A.\ V\"olker, R.\ Dubey, S. M. Linker {\em CHIMIA},75, 6, 555-556 ({\bf 2021}): A perspective on Virtual Events during the Corona Pandemic exemplified by the Career Track with IBM Research Europe - Zurich
\end{enumerate}
