
%DEDICATION
"Home is what you take with you, not what you leave behind."
- N.K. Jemisin, 'The Fifth Season'.


 "Statistics: The only science that enables different experts using the same figures to draw different conclusions."
— Evan Esar.


%----------------------------------------------------------------------------------
%Intro:
\aquote{
    „Dass ich erkenne, was die Welt\\
     Im Innersten zusammenhält, “
}{— Johann Wolfgang von Goethe (1749-1832) }
\input{2_chapter_intro/inc/introduction.tex}

„Lesen ist eine intelligente Methode, sich selber das Denken zu ersparen.“ — Walter Moers, buch Die Stadt der Träumenden Bücher

„Fußnoten sind wie die Bücher im untersten Regal. Die guckt sich keiner gerne an, weil er sich bücken muss.“

%----------------------------------------------------------------------------------
%Ensembler:
\aquote{
``It all works because Avogadro's number is closer to infinity than to 10.''
}
{R. Baierlein ;Gromacs quote collection \cite{Abraham2015}}


%----------------------------------------------------------------------------------
%Restraints
\aquote{
    "Allzu straff gespannt, zerspringt der Bogen."
}{Rudenz, Wilhelm Tell - Friedrich Schiller}

"Restraint! What possible restraint?", "Joseph Conrad"

%----------------------------------------------------------------------------------
%REEDS
"During my undergraduate work I concluded that electrostatics is unlikely to be important [for enzymes]",
"Arieh Warshel, Nobel lecture 2013" 



"It's easy to remember: a half a kT is equal to five fourths of a kJ/mol.",
          "Anders Gabrielsson"
          
"There is no such thing as free energy. Anyone who advocates it does not know what he is talking about.",
          "Alireza Haghighat" 
              
"In this house, we OBEY the laws of thermodynamics!", "Homer Simpson"

%----------------------------------------------------------------------------------
%PygromosChapter

\aquote{
    "Another way of passing the buck is to sacrifice usability on the altar of efficiency."
}{M. Henning,  \cite{Henning2009}}

"I invented the term 'Object-Oriented', and I can tell you I did not have C++ in mind.",
          "Alan Kay, author of Smalltalk"
          
"There are only two things wrong with C++:  The initial concept and the implementation.",
          "Bertrand Meyer"
      
"The determined Real Programmer can write FORTRAN programs in any language.", "Ed Post"

"There are only two kinds of programming languages: those people always bitch about and those nobody uses.",
          "Bjarne Stroustrup" 
          
 "I’ve learned a painful lesson, that for small programs dynamic typing is great. For large programs, you have to have a more disciplined approach. And it helps if the language actually gives you that discipline, rather than telling you, ‘Well, you can do whatever you want." "Guido van Rossum"         
          
%----------------------------------------------------------------------------------
%Cyc Peps
\aquote{
``... everything that living things do can be understood in terms of the jigglings and wigglings of atoms ''
}
{Fundamental assumptions - M. Karplus  and J. A. McCammon \cite{Karplus2002}}




%----------------------------------------------------------------------------------
% Conc & Outlook
\aquote{
`` Wenn ihr's nicht f\"uhlt, ihn werdet's nicht erjagen. ''
}
{w. Goethe, Faust, 13 }

This is the way
mandalorian

„Jede wahre Geschichte ist eine unendliche Geschichte.“ — Michael Ende

Da steh ich nun ich armer Tor! und bin so klug als wie zuvor



%----------------------------------------------------------------------------------
%stuff
\aquote{
    „Je planmäßiger der Mensch vorgeht, um so wirkungsvoller trifft ihn der Zufall.“
}{— Friedrich Dürrenmatt, Die Physiker}

„The way to get good ideas is to get lots of ideas, and throw the bad ones away.“
-Linus Pauling

„If you want to have good ideas you must have many ideas. Most of them will be wrong, and what you have to learn is which ones to throw away.“
-Linus Pauling

Man muss das Unmögliche versuchen, um das Mögliche zu erreichen
Hermann Hesse, Brief (Sept. 1960) an Wilhelm Gundert

"Let us not get carried away with our ideas and take our models too seriously",
          "Nancy Swanson"


"In science it often happens that scientists say, 'You know that's a really good argument; my position is mistaken,' and then they would actually change their minds and you never hear that old view from them again. They really do it. It doesn't happen as often as it should, because scientists are human and change is sometimes painful. But it happens every day. I cannot recall the last time something like that happened in politics or religion.",
          "Carl Sagan"
          
Merk dir eins: Ich bin überall da, wo du mich nicht erwartest, aber niemals da, wo du mich suchst.Walter Moers in Die 13 1/2 Leben des Käpt'n Blaubär 

Das Leben ist zu kostbar, um es dem Schicksal zu überlassen.Leben, MotivationWalter Moers in Die 13 1/2 Leben des Käpt'n Blaubär

“Die Heimat ist da, wo das Herz sein Zuhause hat.”
― Dahi Tamara Koch, Im Ereignishorizont: Gedichte 