\makeatletter
\def\input@path{{../}}
\makeatother
\documentclass[../main.tex]{subfiles}
\begin{document}
\renewcommand{\path}{chapter_2/}
\chapter[
CBTI
]{Alchemical Free-Energy Calculations by Multiple-replica $\lambda$-dynamics: The Conveyor Belt Thermodynamic Integration
}
\chaptermark{CBTI}
\label{ch:cbti}

\aquote{``Let us learn to dream, gentlemen, and then perhaps we
shall learn the truth.''
}
{August Kekul\'e, 1865}

\begin{abstract}
A new method is proposed to calculate alchemical free-energy differences 
based on molecular dynamics (MD) simulations, called the conveyor belt 
thermodynamic integration (CBTI) scheme.
%
As in thermodynamic integration (TI), $K$ replicas of the system are 
simulated at different values of the alchemical coupling parameter $\lambda$.
%
The number $K$ is taken to be even and the replicas are equally spaced
on a forward-turn-backward-turn path, akin to a conveyor belt (CB)
between the two physical end-states.
%
And as in $\lambda$-dynamics ($\lam$D), the $\lambda$-values associated with the 
individual systems evolve in time along the simulation.
%
However, they do so in a concerted fashion, determined by the evolution
of a single dynamical variable $\Lambda$ of period $2\pi$ controlling 
the advance of the entire CB.
%
Thus, a change of $\Lambda$ is always
associated with $K/2$ equispaced replicas moving forward and $K/2$ equispaced
replicas moving backward along $\lambda$.
%
As a result, the effective free-energy profile of the 
replica system along $\Lambda$ is periodic of period $2\pi K^{-1}$
and the magnitude of its variations decreases rapidly
upon increasing $K$, at least as $K^{-1}$ \radd{in the limit of large $K$}.
%
When \radd{a sufficient number of replicas is used}, 
these variations become small, 
which enables a complete and quasi-homogeneous coverage of the $\lambda$-range
by the replica system, without application of any biasing potential. 
If desired, a memory-based biasing potential can still be 
added to further homogenize the sampling, the preoptimization of which 
is computationally inexpensive.
%
The final free-energy profile along $\lambda$ is calculated similarly to TI,
by binning of the Hamiltonian $\lambda$-derivative as a function of $\lambda$ 
considering all replicas jointly, followed by quadrature integration. 
The associated quadrature error can be kept very low owing to 
the continuous and quasi-homogeneous $\lambda$-sampling.
%
The CBTI scheme can be viewed as a \radd{continuous/deterministic/dynamical}
%dynamical 
analog of the Hamiltonian
replica-exchange/permutation (HRE/HRP) schemes, or as a correlated 
multiple-replica analog of the \radd{$\lambda$D or} $\lambda$-local elevation umbrella 
sampling ($\lambda$-LEUS) schemes.
%
Compared to TI, it shares the advantage of the latter schemes 
in terms of enhanced orthogonal sampling, {\em i.e.} the availability of 
variable-$\lambda$ paths to circumvent conformational barriers
present at specific $\lambda$-values.
%
Compared to HRE/HRP, it permits a deterministic and continuous sampling
of the $\lambda$-range, and bypasses the need to carefully
preselect a $\lambda$-ladder \radd{and a swapping-attempt frequency}.
%
Compared to $\lambda$-LEUS, it eliminates (or drastically reduces) 
the dead time associated with the preoptimization
of a biasing potential.
%
The goal of this chapter is to provide the mathematical/physical formulation 
of the proposed CBTI scheme, along with an initial application of the method 
to the calculation of the hydration free energy of methanol.
%
\end{abstract}

\clearpage
\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%================================================================================
\section{Introduction}
%================================================================================

\input{\path/inc/intro.tex}

%================================================================================
\section{Theory}
%================================================================================

\input{\path/inc/theory.tex}

%================================================================================
\section{Computational Details}
%================================================================================

\input{\path/inc/methods.tex}

%================================================================================
\section{Results and Discussion}
%================================================================================

\input{\path/inc/results.tex}

\clearpage
\newpage

%================================================================================
\section{Conclusion}
%================================================================================

\input{\path/inc/conclusion.tex}

\clearpage
\pagebreak

%================================================================================
%\section{Appendix}
%================================================================================
\begin{ethappendix}
\input{\path/inc/appendix.tex}
\end{ethappendix}
\clearpage
\pagebreak

%% %================================================================================
%% \begin{thebibliography}{74}
%% \input{\path/inc/paper.lrs}
%% \end{thebibliography}
%% %================================================================================

\end{document}
