\makeatletter
\def\input@path{{../}}
\makeatother
\documentclass[../main.tex]{subfiles}
\begin{document}
\renewcommand{\path}{3_chapter_1/}
\chapter[Cyclic Peptides Permeability change based on stereocenter changes]{Modulation of the Passive Permeability of Semipeptidic Macrocycles: N- and C-Methylations Fine-Tune Conformation and Properties
    \footnote{\label{footnoteChapter5CopyRight} 
    Reprinted (adapted) with permission from Christian Comeau$^{**}$, Benjamin Ries$^{**}$, Thomas Stadelmann, and et al.,
    J. Med. Chem., \textbf{64}, 5365-5383 (2021). Copyright 2021 American Chemical Society.
    $^{**}$ equal contribution}
}
\chaptermark{Cyclic Peptides}
\label{ch:cycPep}

\aquote{``Let us learn to dream, gentlemen, and then perhaps we
shall learn the truth.''
}
{August Kekul\'e, 1865}




\begin{abstract}
Incorporating small modifications to peptidic macrocycles can have a major influence on their properties. For instance, N-methylation has been shown to impact permeability. A better understanding of the relationship between permeability and structure is of key importance as peptidic drugs are often associated with unfavorable pharmacokinetic profiles. Starting from a semipeptidic macrocycle backbone composed of a tripeptide tethered head-to-tail with an alkyl linker, we investigated two small changes: peptide-to-peptoid substitution and various methyl placements on the nonpeptidic linker. Implementing these changes in parallel, we created a collection of 36 compounds. Their permeability was then assessed in parallel artificial membrane permeability assay (PAMPA) and Caco-2 assays. Our results show a systematic improvement in permeability associated with one peptoid position in the cycle, while the influence of methyl substitution varies on a case-by-case basis. Using a combination of molecular dynamics simulations and NMR measurements, we offer hypotheses to explain such behavior.
%
\end{abstract}

\clearpage
\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%================================================================================
\section{Introduction}
%================================================================================

\input{7_chapter_5/inc/intro.tex}

%================================================================================
\section{Theory}
%================================================================================

\input{7_chapter_5/inc/theory.tex}

%================================================================================
\section{Computational Details}
%================================================================================

\input{7_chapter_5/inc/methods.tex}

%================================================================================
\section{Results and Discussion}
%================================================================================

\input{7_chapter_5/inc/results.tex}

\clearpage
\newpage

%================================================================================
\section{Conclusion}
%================================================================================

\input{7_chapter_5/inc/conclusion.tex}

\clearpage
\pagebreak

%================================================================================
%\section{Appendix}
%================================================================================
\begin{ethappendix}
\input{7_chapter_5/inc/appendix.tex}
\end{ethappendix}
\clearpage
\pagebreak

%% %================================================================================
%% \begin{thebibliography}{74}
%% \input{\path/inc/paper.lrs}
%% \end{thebibliography}
%% %================================================================================

\end{document}
